% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\usepackage{hyperref}

\begin{document}

\name{Mihir P Mehta\\[12pt]} % the \\[12pt] adds a blank line after name

%% \address{Department of Computer Science \\University of Texas at Austin }
\address{Intel Corporation}

\address{+1 512-952-0104 \\ \url{www.cs.utexas.edu/~mihir} }


\begin{resume}

%% \section{Areas of interest}
%% Formal verification, programming languages, operating systems.

\section{Education}
{\bf Ph.D., Computer Science} \hfill (2014 - 2021)\\
University of Texas at Austin\\
GPA: 3.3/4\\
{\bf B.Tech., Computer Science and Engineering} \hfill (2009 - 2013)\\
Indian Institute of Technology (IIT) Delhi\\
GPA: 7.9/10\\
{\bf Exchange semester}, Ecole des Mines, Saint-Etienne \hfill (2011)

\section{Professional Experience}

 {\bf Formal Verification Engineer} at Intel Corporation, Santa Clara,
 CA, USA. \hfill (2021-)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Applying diverse hardware verification tools - Forte,
   JasperGold, ACL2 - to solve a number of verification problems in
   the context of Intel's hardware chips.
 \item Incorporating verification into the hardware development cycle.
 \item Suggesting corrections to hardware designs to speed up the
   process of their verification.
 \end{itemize}

 {\bf Research Intern} at Oracle Corp., Belmont, CA, USA. \hfill (2018)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Completed a code proof to certify the correctness of a highly
   optimised assembly language program.
 \item Contributed to a timing analysis of this program, to ensure the
   avoidance of race conditions.
 \item Studied the potential use of the TLAPS theorem prover for
   distributed systems, and created some preliminary internal
   documentation.
 \end{itemize}

 {\bf Research Intern} at Apple Computer, Inc., Austin, TX,
 USA. \hfill (2017)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Used model checking tools towards verifying Apple's hardware microarchitectures
 \item Developed proofs of correctness of hardware components with
   respect to specifications, with code changes where necessary.
 \end{itemize}

 {\bf Research Intern} at Intel Corporation, Austin, TX, USA. \hfill
 (2015)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Built a Pintool to dynamically analyse executables.
 \item Augmented
   the analysis with fine-grained information obtained from static
   analysis techniques.
 \end{itemize}

 {\bf Software Engineer} at Samsung Research Institute, Noida, India. \hfill (2013-2014)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Optimised the Linux kernel for Samsung's
   Android devices.
 \item Improved core components of the Linux virtual memory subsystem.
 \end{itemize}

\section{Research Experience}

 {\bf Filesystem modelling for FAT32} with Professor William R. Cook, CS department, UT Austin. \hfill (2016-present)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developed a binary-compatible executable model for the FAT32 file system.
 \item Used the model as a basis for separation-based reasoning about
   filesystems and filesystem clients with the ACL2 theorem prover.
 \item Used the separation logic framework as a basis for reasoning
   about concurrent filesystem clients under an oracle model of
   nondeterminism.
 \end{itemize}

 {\bf Program verification in object-oriented languages} with Professors Isil Dillig and Thomas
 Dillig, CS department, UT Austin. \hfill (2014-2015)
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developed a prototype verifier based on Hoare logic and weakest
   pre-conditions.
 \item Used the Soot compiler framework to generate
   verification conditions and the Z3 theorem prover to discharge them.
 \item Generated example
   inputs demonstrating bugs in several test programs.
 \end{itemize}

 {\bf Algorithms for bisimilarity} with Professor S
 Arun Kumar, CSE Department, IIT Delhi    \hfill
 (2012-2013)
 \begin{itemize} \itemsep -2pt
 \item Conceptualised and implemented a toolkit for
   verifying bisimilarity and other properties of timed automata
   and labelled transition systems.
 \item Improved an algorithm for generating a zone
   graph from a timed automaton.

 \end{itemize}

\section{Publications}
  Mihir Parang Mehta. {\bf Formalising Filesystems in the ACL2 Theorem
    Prover: an Application to FAT32}. In: \textit{Proceedings of the
    15th International Workshop on the ACL2 Theorem Prover and Its
    Applications, Austin, Texas, USA, November 5-6, 2018. Electronic
    Proceedings in Theoretical Computer Science.}  Matt Kaufmann and
  Shilpi Goel, editors.  Vol.  280, pp. 18-29, 2018. Full text:
  \url{https://cgi.cse.unsw.edu.au/~eptcs/paper.cgi?ACL22018.2}.

  Mihir Parang Mehta, William R. Cook. {\bf Binary-Compatible
    Verification of Filesystems with ACL2}. In: \textit{10th
    International Conference on Interactive Theorem Proving (ITP 2019)
    (Leibniz International Proceedings in Informatics (LIPIcs))}, John
  Harrison, John O'Leary, and Andrew Tolmach (Eds.), Vol. 141. Schloss
  Dagstuhl-Leibniz-Zentrum fuer Informatik, Dagstuhl, Germany,
  25:1-25:18. Full text:
  \url{https://doi.org/10.4230/LIPIcs.ITP.2019.25}.

  Mihir Parang Mehta, William R. Cook. {\bf Separation Logic-Based
    Verification atop a Binary-Compatible Filesystem Model}. In:
  \textit{23rd Brazilian Symposium on Formal Methods (SBMF 2020)}. Preprint:
  \url{https://hal.archives-ouvertes.fr/hal-02956858}.

  Aarti Gupta, Roope Kaivola, Mihir Parang Mehta, Vaibhav Singh. {\bf
    Error Correction Code Algorithm and Implementation Verification
    using Symbolic Representations}. In: \textit{Formal
    Methods in Computer-Aided Design 2022}. Preprint:
  \url{https://hal.archives-ouvertes.fr/hal-03769882}.

\section{Coursework (selected graduate courses)}
\begin{tabular}{l p{3in}}
  \underline{UT Austin:} Automated Logical Reasoning, Introduction to
  Mathematical Logic, \\ Formal Verification and Semantics, Automatic
  Verification of Software,\\ Numerical Linear Algebra, Dependable
  Computing Sytems, \\Advanced Operating Systems, Recursion and Induction. \\
  \underline{IIT Delhi:} Compiler Design,
  Theory of Computation, Numerical Optimisation.
\end{tabular}

\section{Teaching assistantships (UT Austin)}
\begin{tabular}{l p{3in}}
  \underline{Graduate courses:} \\
  CS386L Programming Languages (Fall 2016, Spring 2020) \\
  Convex Optimization (Fall 2019) \\
  \underline{Undergraduate Courses:} \\
  CS439N Operating Systems (Fall 2015, Spring 2016, Fall 2020) \\
  CS340D Debugging and Verifying Programs (Spring 2018) \\
  CS392F Automated Software Design (Spring 2019) \\
  CS371G Generic Programming (Summer 2020)
\end{tabular}

% Tabulate Technical Skills; p{3in} defines paragraph 3 inches wide
\section{Technical \\ Skills}
   \begin{tabular}{l p{3in}}
    \underline{Theorem provers:} ACL2, Agda, Coq, TLAPS, Forte. \\
    \underline{Other formal verification tools:} JasperGold. \\

    \underline{Programming languages:} Functional languages (OCaml,
    SML), \\ logic programming languages (Prolog),
    hardware description languages (VHDL, Verilog). \\

    \underline{Operating systems:} GNU/Linux (kernel and application development). \\

    \underline{Compiler frameworks:} Soot (Java), LLVM (C++). \\

    \underline{Others:} Xilinx, Matlab, PostgreSQL. \\
 \end{tabular}

\section{Scholastic Achievements}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Awarded the UT Austin Graduate School's Recruitment
   Fellowship. \hfill (2014-2017)
 \item All India Rank 138 (out of 400000), Joint Entrance Examination
   (IIT-JEE). \hfill (2009)
 \item Secured All India Rank 29 in the All India Engineering Entrance
   Examination (AIEEE) among 1000000 candidates.\hfill (2009)
 \item Scored 99 percentile in Verbal and Analytical Reasoning,
   GRE. \hfill (2012)
 \end{itemize}

\section{Others}
\begin{tabular}{l p{3in}}
  \underline{Languages:} English, French, Gujarati, Hindi. \\
\end{tabular}

\end{resume}
\end{document}
